---
title: "Untitled"
author: "Huang Tao"
date: "2020/3/12"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}


library(ggplot2)

# 100 random numbers from standard norm 
data <- data.frame(value =rnorm(100))

ggplot(data, aes(x=value)) + 
  geom_histogram()

```





```{r}

# library
library(ggplot2)
library(dplyr)

# Build dataset with different distributions
data <- data.frame(
  type = c( rep("variable 1", 1000), rep("variable 2", 1000) ),
  value = c( rnorm(1000), rnorm(1000, mean=4) )
)

# Represent it
p <- data %>%
  ggplot( aes(x=value, fill=type)) +
    geom_histogram( color="#e9ecef", alpha=0.6, position = 'identity')



p


```


















## R markdown

R markdown is an interactive report for R code.

* Text formating

write in **bold** or *italic*

add horizontal line by adding 3 stars:

***

add 3 blank lines
<br><br><br>

solve the probelm of too much white space around image
library(png)
library(grid)
img <- readPNG('')
grid.raster(img)

{r, fig.align='center', fig.width=6,fig.height=6,fig.cap='Fig.1 This is a figure.'}

* Insert equation in **Latex** formating

$A = (\pi * \lambda \times r^{4} ) / \alpha$


* Layout of image is set in {r, out.width = c('50%', '50%')}


## A

content

## B

content #2

## C 


## First
A first section

## Second
content of sub-chapter #2

## Third
content of sub-chapter #3
content #3

